Response to the defense feedback

### 2021-06-23 Chapter-1/Chapter-1.tex
last revision from D.

\chapter{Introduction} \label{chapter1}
Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with less than one hundred thousand lines of code. 
Today, a mobile instant messaging (IM) application such as Telegram~\cite{telegram} contains more than two million lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}. The complexity in today's software systems makes it hard for developers to understand the codebase and find defects manually. So an automated bug detection tool is often needed. In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications. The side-channel vulnerability is a type of information leakage bugs in software systems. Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself. So it is sometimes harder for developers to identify side-channel vulnerabilities.

>>>>

\chapter{Introduction} \label{chapter1}
Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with less than one hundred thousand lines of code. 
Today, a mobile instant messaging (IM) application such as Telegram~\cite{telegram} contains more than two million lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}. The complexity in today's software systems makes it hard for developers to understand the codebase and find defects manually. So an automated %bug detection
tool is often needed. In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications. 
%The side-channel vulnerability is a type of information leakage bugs in software systems. Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself. So it is sometimes harder for developers to identify side-channel vulnerabilities.

### 2021-06-23 Chapter-6/Chapter-6.tex
last revision from D.

\chapter{Discussion and Limitations}\label{chapter6}
\section{Fast and Precise Side-channel Vulnerability Detection}
\subsection*{Code Coverage} \detect{} analyzes one x86 execution trace each time. The design is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, but shares common limitations of dynamic approaches. \detect{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may miss some side-channel vulnerabilities not covered by the analyzed trace. However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage under various inputs. The evaluation result also confirms the above intuition. For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation. RSA implementations have several secret-dependent control-flow transfers. Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

@@

\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them are not patched by developers.
Side-channels are ubiquitous in software, and it is difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def} in Chapter~\ref{chapter4}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def} in Chapter~\ref{chapter4}, it means the leakage is very severe. 
\section{Precise Analysis on Multiple-trace Attacks}
In this work, we present an approach that tries to give an 
estimation of the amount of leaked information by access-based
side-channel attacks. These attacks exploit the data-flow from secrets
to load address and the data-flow from the data-flow from secrets to
branch conditions to retrieve secrets based on the observation on the
memory accesses. Although these kinds of side-channel leakages have
been discovered for decades, the up-to-date software still has some
side-channel leakages. For some of these vulnerabilities, developers
do not fix them because they think these side-channel vulnerabilities
are not important. To show the importance of these side-channel
leakages, one way is to demonstrate an end-to-end attack based on the
vulnerability. However, demonstrating an end-to-end attack often need
a lot of manual effort and the domain knowledge of the victim program,
which is not often the case in practice. It is good to have a tool
that automatically assesses the severity level of these side-channel
leakages. So it would be better to have a proper metric to quantify
the side-channel leakage. However, we find previous side-channel
quantification tools are developed to ensure the noninterference of
the program. They use the over-approximation heuristics method to
quantify the leakage. For example, CacheAudit estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even these
tools report severe leakage, it does not mean the program has a truly
severe leakage.

>>>>

\chapter{Discussion and Limitations}\label{chapter6}
%\section{Fast and Precise Side-channel Vulnerability Detection}
\section{Side-channel Vulnerability Detection}
\subsection*{Code Coverage} \detect{} analyzes one x86 execution trace each time. The design is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, but shares common limitations of dynamic approaches. \detect{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may miss some side-channel vulnerabilities not covered by the analyzed trace. However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage under various inputs. The evaluation result also confirms the above intuition. For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation. RSA implementations have several secret-dependent control-flow transfers. Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

@@

%\section{Precise Analysis on Single-trace Attacks}
\section{Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them are not patched by developers.
Side-channels are ubiquitous in software, and it is difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def} in Chapter~\ref{chapter4}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def} in Chapter~\ref{chapter4}, it means the leakage is very severe.

%\section{Precise Analysis on Multiple-trace Attacks}
\section{Analysis on Multiple-trace Attacks}
In this work, we present an approach that tries to give an 
estimation of the amount of leaked information by access-based
side-channel attacks. These attacks exploit the data-flow from secrets
to load address and the data-flow from the data-flow from secrets to
branch conditions to retrieve secrets based on the observation on the
memory accesses. Although these kinds of side-channel leakages have
been discovered for decades, the up-to-date software still has some
side-channel leakages. For some of these vulnerabilities, developers
do not fix them because they think these side-channel vulnerabilities
are not important. To show the importance of these side-channel
leakages, one way is to demonstrate an end-to-end attack based on the
vulnerability. However, demonstrating an end-to-end attack often need
a lot of manual effort and the domain knowledge of the victim program,
which is not often the case in practice. It is good to have a tool
that automatically assesses the severity level of these side-channel
leakages. So it would be better to have a proper metric to quantify
the side-channel leakage. However, we find previous side-channel
quantification tools are developed to ensure the noninterference of
the program. They use the over-approximation heuristics method to
quantify the leakage. For example, CacheAudit estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even these
tools report severe leakage, it does not mean the program has a truly
severe leakage.
